---
title: "W_UP_01"
author: "Kaylie Brehm"
date: "summer 2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
Position is a categorical variable. Push-ups are a numerical variable. I will do an numerical analysis on push-ups in correlation to position.


# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(pushups~position,data=mydata)
```

The Y-Axis shows number of pushups. The X-Axis shoes the position. Each whisker plot shows averages within data There does seem to be a difference in number of pushups for each position.

### Numerical Descriptive Results



<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```

The difference between pushup ability in the line position players and skill position players is made apparent when comparing the median and means. The line players had a median of 14.5 and a mean of 17.1 pushups. The skill players had a median of 47.5 and a mean of 49.7 pushups. So far, it seems that skill players achieve far more pushups.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(pushups~position,data=mydata)
```

The data above shows, once again, a difference in pushup number with each position. The t value is -5.4341. The df value is 27.079. The p-value is 0.000009421. It was assumed in the alternative hypothesis that there would be a difference with pushup number between  positions. In analyzing the pushup numbers between two positions, we came up with data that the line players have a mean of 17.1 and the skill players have a mean of 49.7. This hypothesis has sufficient support. Furthermore, since the p-value is so small, I reject the null hypothesis, that there was no difference.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

